---
title: "Week 10"
author: "Group 3: Mara Alexeev, Parker Bannister, Mitchell Flagg"
date: "November 16, 2020"
output: html_document

---


**Deliverables:**

Code available at our github repo: [MaraAlexeev/720_regex_mmp](https://github.com/MaraAlexeev/720_regex_mmp)

[Error analysis](#eval) of the top 10 false positive and false negative terms

Model Output - group3_predictions_wk10.csv
linear model output:
xgboost model output: 




# Libraries
```{r libraries, warning=FALSE, message=FALSE}
#get relevant libraries
library(tidyverse)
library(forcats)
#install.packages("caret")
#library(caret)
#install.packages("rlang")
#install.packages("cvms")
#install.packages("cvms")
library(cvms)
#install.packages("tidyr")
library(tidyr)
#library(broom)    
library(tibble)   
#install.packages("here")
library(here)
#library(tidytext)
#install.packages("ggimage")
library(ggimage)
#install.packages("rsvg")
library(rsvg)
#library(textstem)
library(text2vec)
library(data.table)
require(xgboost)
require(Matrix)

#install.packages("glmnet")
#library(glmnet)
library(ROCR)
library(pROC)
library(caTools)
library(tm)
library(SnowballC)
```

# Functions
```{r custom functions, echo=FALSE}

search_assign_by_cc <- function(data, search_terms, column_to_search) {
  pasted_match <- paste(search_terms, collapse = "|")
  
  searched_and_assigned <- data %>%
  mutate(covid_guess = as.integer(grepl(pattern = pasted_match, x = column_to_search, ignore.case = TRUE))) 
  
  return(searched_and_assigned)
}

covid_prediction_count <- function(data) {
  prediction_count <- data %>% 
  group_by(covid_guess) %>%
  summarise(count = n())
  
  return(prediction_count)
}

covid_model_comparison <- function(data_predictions, data_w_labels) {
  only_labeled_rows <- data_w_labels %>%
    filter(label == "0"| label == "1")
  
  joined_data <- only_labeled_rows %>%
  left_join(data_predictions, by = "id") 
  
  joined_data$label <- as.numeric(joined_data$label)
  
  renamed_joined_data <- joined_data %>% 
  rename(
    covid_status = label,
    covid_prediction = covid_guess
    )
  
  error_analysis <- renamed_joined_data %>%
 mutate(results =  case_when(
    covid_status == 0 & covid_prediction == 0 ~ "True Negative",
    covid_status == 1 & covid_prediction == 1 ~ "True Positive",
    covid_status == 0 & covid_prediction == 1 ~ "False Positive",
    covid_status == 1 & covid_prediction == 0 ~ "False Negative"
  )
 )
  return(error_analysis)
}

covid_model_comparison_table <- function(data_with_status_and_prediction){
  real_and_prediction <- data_with_status_and_prediction %>%
  group_by(covid_status, covid_prediction) %>%
  summarise(count = n())
  
   return(real_and_prediction)
}

evaluation_table <- function(covid_model){

model_basic_table <- data.frame("target" = c(covid_model$covid_status),
                                  "prediction"= c(covid_model$covid_prediction)) 

model_eval <- evaluate(model_basic_table,
                 target_col = "target",
                 prediction_col = "prediction",
                 type = "binomial")

return(model_eval)
}

#Function to sort results by cc

cc_by_results <- function(model, results_factor, cc_number_to_return = 10) {
  results_filtered <- model %>%
  filter(results == results_factor)
  
  top_cc <- results_filtered%>%
  group_by(results, cc) %>%
  summarise(count = n()) %>% 
  arrange(desc(count)) %>%
  head(cc_number_to_return)
  

  return(print(top_cc))
}
```

## Load data files
```{r load files, warning=FALSE, message=FALSE}

covidclass_70percentlabels <- read.table("data_do_not_alter/covidclass_70percentlabels.csv",  na.strings = "", header = TRUE, sep = "|", quote = "", comment.char = "", col.names = c("id", "chief_complaint_1", "chief_complaint_2", "thirty_label", "seventy_label"))

cclist <- read_delim("ontology/presentingproblem/CCList.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

qalist <- read_delim("ontology/presentingproblem/QAList.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

concepts <- read_delim("ontology/presentingproblem/concepts.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)

relationship <- read_delim("ontology/presentingproblem/relationship.tsv", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
```

## Clean Data
```{r clean data}

#Cleaning rows 4010 and 6713 with extra quotation marks
covidclass_70percentlabels[4010,1] <- 4010 
covidclass_70percentlabels[4010,5] <- 0 
covidclass_70percentlabels[6713,1] <- 6713
covidclass_70percentlabels[6713,5] <- 0 

#Making empty chief complaint clearer
covidclass_70percentlabels$chief_complaint_1[which(is.na(covidclass_70percentlabels$chief_complaint_1))] <-  "No CC provided"

covidclass_70percentlabels$id <- as.numeric(covidclass_70percentlabels$id)

#Clean column names and drop unneeded columns

covid_dataset <- covidclass_70percentlabels %>% 
   mutate(covid_label = case_when(
    seventy_label == "0" ~ 0,
    seventy_label == "1" ~ 1
  )) %>% 
  rename(cc = chief_complaint_1) %>% 
  select(c("id", "cc", "covid_label")) 
```

# New Concept mapping

Must keep the final dataset named covid_dataset to work with further analysis code below.
```{r}

```


```{r combine ccs}

#Combine concepts that are similar but different encodings of the same chief complaint to account for different spellings and misspellings or abbreviations

# sob_concept <- c("SOB", 	"SOB - SHORTNESS OF BREATH", "SHORT OF BREATH", "SHORT OF BREATHE", "SHORTNESS OF BREATH")
# fever_concept <- c("FEVER", "FEVERS")
# ili_concept <- c("\\bILI\\b", "FLU", "FLU-LIKE SYMPTOMS", "ILI - INFLUENZE LIKE ILLNESS", 	"INFLUENZA LIKE ILLNESS", "INFLUENZA", "I L I", "ILI")
# cough_concept <- c("COUGH", "COUGH/CONGESTION", "Productive cough", "PRODUCTIVE COUGH")
# hypoxia_concept <- c("HYPOXEMIA", "HYPOXIA", "HYPOXIC")
# dyspnea_concept <- c("DYPNEA", "DYSPNEA")
# doe_concept <- c("DOE - DYSPNEA ON EXERTION", "DYSPNEA ON EXERTION")
# resp_dis_concept <- c("RESP DISTRESS", 	"RESPIRATORY DISTRESS")
# 
# combined_cc_data <- covidclass_70percentlabels %>% 
#   mutate(grouped_cc = case_when(
#     chief_complaint_1 %in% sob_concept ~ "shortness of breath",
#     chief_complaint_1 %in% fever_concept ~ "fever",
#     chief_complaint_1 %in% ili_concept ~ "ili",
#     chief_complaint_1 %in% cough_concept ~ "cough",
#     chief_complaint_1 %in% hypoxia_concept ~ "hypoxia",
#     chief_complaint_1 %in% dyspnea_concept ~ "dyspnea",
#     chief_complaint_1 %in% doe_concept ~ "doe",
#     chief_complaint_1 %in% resp_dis_concept ~ "respiratory distress",
#     TRUE                           ~ .$chief_complaint_1
#     )
#   )


```

## Create labeled datasets
```{r}
labeled_data <- covid_dataset %>% 
  filter(!is.na(covid_label)) 

```


## xgboost analysis pipeline
# Create a corpus for labeled data
```{r corpus creation}
#https://www.pluralsight.com/guides/machine-learning-text-data-using-r

corpus <-  Corpus(VectorSource(labeled_data$cc))
corpus[[1]][1]  

corpus <-  tm_map(corpus, PlainTextDocument)

corpus  <-  tm_map(corpus, tolower)
  

corpus <- tm_map(corpus, removePunctuation)
corpus[[1]][1]  

corpus <-  tm_map(corpus, removeWords, c(stopwords("english")))
corpus[[1]][1] 

corpus <-  tm_map(corpus, stemDocument)
corpus[[1]][1] 

frequencies  <-  DocumentTermMatrix(corpus)

#Choose value for your sparse terms cutoff
sparse_term_cutoff <- 0.995

sparse <-  removeSparseTerms(frequencies, sparse_term_cutoff)

tSparse <-  as.data.frame(as.matrix(sparse))
colnames(tSparse) <-  make.names(colnames(tSparse))

columns_to_keep <- colnames(tSparse)

# Add back covid label to sparse term dataframe 
tSparse$covid_label <-  labeled_data$covid_label
```
## Test and Train data for xgboost
```{r divide to test and train}

set.seed(888)
split  <-  sample.split(tSparse$covid_label, SplitRatio = 0.7)
trainSparse  <-  subset(tSparse, split==TRUE)
testSparse <-  subset(tSparse, split==FALSE)


```

## Non linear model with xgboost

### Train model
```{r}

#Drop the covid_label from being in the training
data_matrix <- as.matrix(trainSparse[,colnames(trainSparse) != "covid_label"])
output_vector  <-  as.matrix(trainSparse[,"covid_label"]) 

bst <- xgboost(data = data_matrix, label = output_vector, scale_pos_weight = 20, nrounds = 20,objective = "binary:logistic")
```

### Use test data
```{r}

data_matrix_test <- as.matrix(testSparse[,colnames(testSparse) != "covid_label"])

pred <- predict(bst, data_matrix_test)


# Pick a prediction cutoff
prediction_cutoff <- 0.5
prediction <- as.numeric(pred > prediction_cutoff)
```

```{r}

test_data <- data.frame(testSparse)
test_data <- rownames_to_column(test_data, var = "id")
prediction <- data.frame(prediction)

data_and_prediction <-cbind(test_data, prediction)

small_d_and_p <- data_and_prediction %>% 
  select("id", "prediction", "covid_label")

#Small confusion matrix
table(small_d_and_p$prediction, small_d_and_p$covid_label)
```



```{r}
corpus_f <-  Corpus(VectorSource(covid_dataset$cc))

corpus_f <-  tm_map(corpus_f, PlainTextDocument)

corpus_f  <-  tm_map(corpus_f, tolower)

corpus_f <- tm_map(corpus_f, removePunctuation)


corpus_f <-  tm_map(corpus_f, removeWords, c(stopwords("english")))

corpus_f <-  tm_map(corpus_f, stemDocument)
 

frequencies_f  <-  DocumentTermMatrix(corpus_f)

frequencies_f_all_columns <-  as.data.frame(as.matrix(frequencies_f))

full_data_top_columns <- frequencies_f_all_columns %>% 
  select(columns_to_keep)


full_data_top_columns$covid_label <-  (covid_dataset$covid_label)

data_matrix_full <- as.matrix(full_data_top_columns[,colnames(full_data_top_columns) != "covid_label"])

pred_full <- predict(bst, data_matrix_full)
pred_full <- data.frame(pred_full)
```

## Predicted probabilities and cutoff
```{r}
covid_dataset$model_predictions <- pred_full$pred_full

covid_dataset <- covid_dataset %>% 
  mutate(final_predictions = case_when(
    model_predictions >= prediction_cutoff ~ 1,
    model_predictions < prediction_cutoff ~ 0,
  ))

predictions_errors <- covid_dataset %>% 
  filter(!is.na(covid_label))

table(predictions_errors$covid_label, predictions_errors$final_predictions)
```
## ROC curves
```{r}
prediction_xgboost_model <- prediction(predictions_errors$final_predictions, predictions_errors$covid_label)

performance_xgboost_model <- performance(prediction_xgboost_model,"tpr","fpr")
plot(performance_xgboost_model,colorize=FALSE)
```
```{r}
pROC_obj <- roc(predictions_errors$final_predictions, predictions_errors$covid_label,
            smoothed = TRUE,
            # arguments for ci
            ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)


sens.ci <- ci.se(pROC_obj)
plot(sens.ci, type="shape", col="lightblue")
## Warning in plot.ci.se(sens.ci, type = "shape", col = "lightblue"): Low
## definition shape.
plot(sens.ci, type="bars")
```


```{r}
model_xgboost <- data.frame("target" = c(predictions_errors$covid_label),
                                  "prediction"= c(predictions_errors$final_predictions)) 

model_eval_model_xgboost <- evaluate(model_xgboost,
                 target_col = "target",
                 prediction_col = "prediction",
                 type = "binomial")

```


# Comparisons
```{r}
model_eval_model_xgboost[,1:7]
```

From Peter
Week 8 results on test: 


* sensitivity    0.285714286
* specificity    0.864125122
* PPV    0.122105263
* NPV    0.948158742
* accuracy    0.828239609
* f1    0.171091445



# Error Analysis {#eval}


```{r}
error_analysis <- predictions_errors %>%
 mutate(results =  case_when(
    covid_label == 0 & final_predictions == 0 ~ "True Negative",
    covid_label == 1 & final_predictions == 1 ~ "True Positive",
    covid_label == 0 & final_predictions == 1 ~ "False Positive",
    covid_label == 1 & final_predictions == 0 ~ "False Negative"
  ))
```

```{r, message = FALSE}

tp_model_1 <- cc_by_results(error_analysis, "True Positive")
tn_model_1 <- cc_by_results(error_analysis, "True Negative") 
fp_model_1 <- cc_by_results(error_analysis, "False Positive") 
fn_model_1 <- cc_by_results(error_analysis, "False Negative") 

all_results_model_1 <- bind_rows(tp_model_1, tn_model_1, fp_model_1, fn_model_1)

all_results_model_1_wide <- pivot_wider(all_results_model_1, names_from = results, values_from = count, values_fill = 0)




```



## xgboost model Output
```{r}
#Our COVID prediction is labeled in the column final_predictions
group3_predictions_wk10_xgboost <- covid_dataset 
write_csv(group3_predictions_wk10_xgboost, "./analysis/group3_predictions_wk10_xgboost")
```

### Session Information
```{r session information}
sessionInfo()
```
