---
title: "Week 6 with Functions!"
author: "Group 3"
date: "10/17/2020"
output: html_document
---

**Deliverables:**
Code available at our github repo: [MaraAlexeev/720_regex_mmp](https://github.com/MaraAlexeev/720_regex_mmp)

Error analysis of the top 10 false positive and false negative terms

Model Output - same as prior week

Write a paragraph as to which metric you are trying to optimize for (sensitivity, specificity, PPV, NPV, accuracy, or F1-score)



```{r libraries, warning=FALSE, message=FALSE}
#get relevant libraries
library(tidyverse)
library(forcats)
library(caret)
library(cvms)
library(broom)    
library(tibble)   
library(here)
library(tidytext)
library(ggimage)
library(rsvg)
```

```{r custom functions}

search_assign_by_cc <- function(data, search_terms, column_to_search) {
  pasted_match <- paste(search_terms, collapse = "|")
  
  searched_and_assigned <- data %>%
  mutate(covid_guess = as.integer(grepl(pattern = pasted_match, x = column_to_search, ignore.case = TRUE))) 
  
  return(searched_and_assigned)
}

covid_prediction_count <- function(data) {
  prediction_count <- data %>% 
  group_by(covid_guess) %>%
  summarise(count = n())
  
  return(prediction_count)
}

covid_model_comparison <- function(data_predictions, data_w_labels) {
  only_labeled_rows <- data_w_labels %>%
    filter(label == "0"| label == "1")
  
  joined_data <- only_labeled_rows %>%
  left_join(data_predictions, by = "id") 
  
  joined_data$label <- as.numeric(joined_data$label)
  
  renamed_joined_data <- joined_data %>% 
  rename(
    covid_status = label,
    covid_prediction = covid_guess
    )
  
  return(renamed_joined_data)
}

covid_model_comparison_table <- function(data_with_status_and_prediction){
  real_and_prediction <- data_with_status_and_prediction %>%
  group_by(covid_status, covid_prediction) %>%
  summarise(count = n())
  
  error_analysis <- real_and_prediction %>%
 mutate(results =  case_when(
    covid_status == 0 & covid_prediction == 0 ~ "True Negative",
    covid_status == 1 & covid_prediction == 1 ~ "True Positive",
    covid_status == 0 & covid_prediction == 1 ~ "False Positive",
    covid_status == 1 & covid_prediction == 0 ~ "False Negative"
  )
 )
  return(error_analysis)
}

evaluation_table <- function(covid_model){

model_basic_table <- data.frame("target" = c(covid_model$covid_status),
                                  "prediction"= c(covid_model$covid_prediction)) 

model_eval <- evaluate(model_basic_table,
                 target_col = "target",
                 prediction_col = "prediction",
                 type = "binomial")

return(model_eval)
}
```

## Load data files
```{r load files, warning=FALSE, message=FALSE}
#read in data and print
covidclass_without_labels <- read_csv("data_do_not_alter/covidclass_without_labels.csv")
covidclass_w_labels <- read_csv("data_do_not_alter/covidclass_30_percent_labels.csv")
```

## Clean Data
```{r clean data}

clean_data <- covidclass_without_labels %>%
  mutate(id_cc = `patientID|chief complaint|`) 

clean_data <- clean_data %>%
  separate(col = id_cc, into = c('id', 'cc1', 'cc2'), sep = "[|]", remove = F)

clean_data$cc1 <- as_factor(clean_data$cc1)

clean_labeled_data <- covidclass_w_labels %>%
  mutate(id_label_cc = `patientID|labels|chief complaint|`) 

clean_labeled_data <- clean_labeled_data %>%
  separate(col = id_label_cc, into = c('id', 'label', 'cc1', 'cc2'), sep = "[|]", remove = F)

clean_labeled_data$cc1 <- as_factor(clean_labeled_data$cc1)
```

## Initial Search Terms 
```{r Initial Search Terms, message=FALSE}
cc_to_match <- c("short", "fever", "i l i", " ili ", "\\bili\\b","influe", "covid", "HYPOXIA", "DYSPNEA", "SOB", "cough", "DOE")

predicted_covid_1 <- search_assign_by_cc(clean_data, cc_to_match, clean_data$cc1)

covid_prediction_counts_1 <- covid_prediction_count(predicted_covid_1)
covid_prediction_counts_1
```

## Initial Model Performance
```{r first model performance}

model_1 <- covid_model_comparison(predicted_covid_1, clean_labeled_data)
model_1_table <- covid_model_comparison_table(model_1)
model_1_table
```

```{r}
plot_confusion_matrix(model_1_table,
                      targets_col = "covid_status",
                      predictions_col = "covid_prediction",
                      counts_col = "count")
```

```{r}

model_1_evaluated <- evaluation_table(model_1)
model_1_evaluated

```


## Analysis pipeline

Do not modify this. Copy it and place in new chunk for each set of words used in analysis. Follow directions in each commented line.
```{r do not modify, eval=FALSE}

#choose your search terms
cc_to_match <- c("short", "fever", "i l i", " ili ", "\\bili\\b","influe", "covid", "HYPOXIA", "DYSPNEA", "SOB", "cough", "DOE")

#change object name. replace each "example" with your model's name. 13 places. Want to figure out a better way to do this.

predicted_covid_example <- search_assign_by_cc(clean_data, cc_to_match, clean_data$cc1)

covid_prediction_counts_example <- covid_prediction_count(predicted_covid_example)
covid_prediction_counts_example

model_example <- covid_model_comparison(predicted_covid_example, clean_labeled_data)
model_example_table <- covid_model_comparison_table(model_example)
model_example_table

plot_confusion_matrix(model_example_table,
                      targets_col = "covid_status",
                      predictions_col = "covid_prediction",
                      counts_col = "count")

model_example_evaluated <- evaluation_table(model_example)
model_example_evaluated 
```


### Session Information
```{r session information}
sessionInfo()
```

